Social Participation Ontology: community documentation, enhancements and use examples

### 2015-09-20 plosOne/cover/coverLetter.tex
terminada formatacao da cover letter
reviewed cover letter

\namefrom{Renato Fabbri} % Name

@@

	Please find attached the manuscript entitled "Social Participation Ontology: community documentation, enhancements and use examples", which we submit for publication in the PLOS ONE Journal. The reasons why we chose PLOS ONE as the vehicle for our manuscript are as follows.
	In the manuscript we report the development of a participatory upper OWL ontolgy.
	We were unable to find similar conceptualization in literature, although consistent with other upper ontologies and characterizations of such social structures.
	The ontologic structures have had some uses in linked data sharing and conceptual maturing.
	Handpicked examples are the use by the Brazilian social participation portal for sharing linked data
	and the international process of first conceptualizations.
	This document have been used as a reference by community but lacks a peer review chancel.
	All data, scripts and documentation are open since first versions, including the submited article.
	Processes are also kept open, with traces in git repositories, data repositories,
	dedicated portals, and specialized gadgets.
	Because the methods and results are multidisciplinary, compliant with open information standards and with aplications of public interest,
	we take the view that the manuscript may be of interest to a very wide readership.
	 We believe that NJP is therefore the ideal vehicle for this type of scientific contribution.
	 If
	 you feel that the manuscript is appropriate for your journal, we suggest the following reviewers: 
	 Tudor Groza,
	 Indra Neil Sarkar,                                                        and 
	 Chris Mavergames.

@@

\end{newlfm}
\end{document}

>>>>

\namefrom{\includegraphics[width=0.2\textwidth]{assinatura-2011-07-06__}\newline\newline Renato Fabbri} % Name

@@

	Please find attached the manuscript entitled "Social Participation Ontology: community documentation, enhancements and use examples", which we submit for publication in the PLOS ONE Journal. The reasons why we chose PLOS ONE as the vehicle for our manuscript are as follows.
	In the manuscript we report the development of a participatory upper OWL ontology.
	We were unable to find similar conceptualization in literature, although consistent with other upper ontologies and characterizations of such social structures.
	The ontologic structures have had some uses in linked data sharing and conceptual maturing.
	Handpicked examples are the use by the Brazilian federal social participation portal for sharing linked data
	and the international process of first conceptualizations.
	This research article have been used as a reference by community but lacks a peer review chancel.
	All data, scripts and documentation are open since first versions, including the submitted article.
	Processes are also kept open, with traces in git repositories, data repositories,
	dedicated portals, and specialized gadgets.
	Because the methods and results are multidisciplinary, compliant with open information standards and with applications of public interest,
	we take the view that the manuscript may be of interest to a very wide readership.
	 We believe that PLOS ONE is therefore the ideal vehicle for this type of scientific contribution.
	 If
	 you feel that the manuscript is appropriate for your journal, we suggest the following reviewers: 
	 Tudor Groza,
	 Indra Neil Sarkar,                                                        and 
	 Chris Mavergames.

%
%	 \begin{figure}[!h]
%%		         \includegraphics[width=0.1\textwidth]{assinatura-2011-07-06_}
%		 \centering
%		         \includegraphics[width=0.1\textwidth]{assinatura-2011-07-06_}
%		 \end{figure}
%

@@

%----------------------------------------------------------------------------------------
\end{newlfm}
\end{document}
